\documentclass[a4paper]{article}

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{enumitem}
\usepackage{verbatim} % for multiline comments

\title{System Validation: Project}
\author{J.M. Somers, C. Roest, D. van den Heuvel \& I.C.T.M Speek}

\begin{document}
\maketitle

%----------------------------------------------------------------%

\begin{comment}
  \begin{abstract}
  Your abstract.
  \end{abstract}
\end{comment}

%----------------------------------------------------------------%

\section{Introduction}
\label{sec:introduction}
\input{introduction}			% introduction.tex wordt hier geimporteerd
% intoductie tot complexiteit brug systemen
% wat moet de safety controller kunnen
% onze taken
% introductie tot parallele componenten en architectuur
% verwijzen naar wat er in elke sectie gebeurt


%----------------------------------------------------------------%
\newpage
\section{The model}
\label{sec:model}
\todo{Make own images}
\input{model}
% Give an introduction to the situational sketch and model system
% Present the communication model
% Argument design choices

\subsection{Objects}
\label{sec:objects}
\todo{argument objects and their numbers}

\begin{enumerate}

\item{Control system} \\
The system that gives the instructions to the safety controler for "when" actions have to be done. 
\begin{itemize}
\item{User}
\item{Interface Controller} 
\end{itemize}
output: Unsafe actions to control the different elements of the bridge. \\
actions: The user (or any other system behind the interface controler) determines when different actions should take place. \\
input: status of the other subsystems. 

\item{Safety controller} \\
The system that checks if the given actions from the control system are safe according to the status of the different components. 
\begin{itemize}
\item{contains no other objects} 
\end{itemize}
output: safe actions to control the different elements of the bridge, is able to report status errors to the control system. \\
actions: Check status of different objects. \\
input: unsafe actions. 

\item{Bridge-deck system}
\begin{itemize}
\item{3 sensors: Bridge is open}
\item{3 sensors: Bridge is closed}
\item{3 sensors: Bridge locking pins state}
\item{2 locking pins}
\item{Bridge break}\item{Bridge motor. This also indicates a state \{Stopped, Moving up, moving down, broken\}}
\end{itemize}
input: action requests for opening or closing the bridge. \\
actions: control the right sequence of brigde-objects to open or close the bridge\\
output: status of different components. 

\item{Light system}
\begin{itemize}
\item{2 orange Lights for lane 1}
\item{2 orange Lights for lane 2}
\item{2 red Lights for lane 1}
\item{2 red Lights for lane 2}
\end{itemize}
input: Status request of the lights, or action request to change the status of the lights \\
actions: change the status of the lights\\
output: Status of the different lights:\{on, off, broken\}.
 

\item{barier system}
\begin{itemize}
\item{inner barier 1}
\item{outer barier 1}
\item{2 sensors for if inner barier of lane 1 is open}
\item{2 sensors for if outer barier of lane 1 is open}
\item{2 sensors for if inner barier of lane 1 is closed}
\item{2 sensors for if outer barier of lane 1 is closed}
\item{inner barier 2}
\item{outer barier 2}
\item{2 sensors for if inner barier of lane 2 is open}
\item{2 sensors for if outer barier of lane 2 is open}
\item{2 sensors for if inner barier of lane 2 is closed}
\item{2 sensors for if outer barier of lane 2 is closed}
\end{itemize}
input: actions to control the different objects of the barier system. \\
actions: change state of objects of the barier system. \\
output: status of objects of the barier system. 

%----------------------------------------------------------------%

\end{enumerate}

\subsection{Definitions}
\label{sec:definitions}

\begin{enumerate}
\item{The bridge is open if the 2 out of 3 sensors indicate that the bridge is open.}
\item{The bridge is closed if the 2 out of 3 sensors indicate that the bridge is closed.}
\item{The bridge is in undefined state when the bridge is not open and not closed.}
\item{When the input of the safety controller issues to open the bridge, the bridge is going to be opened in precise order discribed in \ref{openBridge}}
\item{When the input of the safety controller issues to open the bridge, the bridge is going to be opened in precise order discribed in \ref{closeBridge}}
\item{Traffic flow is hampered when the bridge is in a state where both cars and vessels cannot cross.}
\item{The barriers that the cars will encounter first will be called "first barriers"}
\item{The barriers that the cars will encounter last will be called "last barriers"}

\end{enumerate}



%----------------------------------------------------------------%

\section{Requirements}
\label{sec:requirements}

Case: bridge is going to be opened
\label{openBridge}
\begin{enumerate}

\item{The red lights may not go on if the yelow lights are not already on.}
\item{The barriers may not close if the red lights are not on.}
\item{\label{item:traffic}If there is traffic on the bridge, the bariers may not close.}
%\item{The bridge may not open if the barriers are not closed.}
\item{The last barriers can close if and only if the first barriers are closed.}
\item{The bridge may not open if not all barriers are closed.}
\item{The bridge may not open if the locking pins are engaged.}

\end{enumerate}


\noindent Case: bridge is going to be closed
\label{closeBridge}
\begin{enumerate}[resume]

\item{The barriers may not open if the bridge is not closed.}
\item{The red lights may not go out when the bariers are not up.}
\item{The locking pins may not engage if the bridge is not closed.}

%\item{The bridge may not close if the ship has not completely passed the bridge.}


\end{enumerate}

\noindent General Requirements

\begin{enumerate}[resume]

\item{The break must be applied if the bridge is open and is not going to close}
\item{The break must be applied if the bridge is closed and is not going to open}
\item{If the motor is broken, the brake must be aplied.}
%\item{Road traffic may not cross the bridge if the locking pins are not engaged.}
\item{The flow of the traffic may only be hampered if this cannot be avoided.}

\end{enumerate}

\newpage



%----------------------------------------------------------------%

\section{Questions}

\begin{enumerate}

\item{Is de break "smart" en kan zijn status worden opgevraagd?}

\item{Does the bridge need a safety break and a safety motor?}

\item{Zijn er genoeg paralelle componenten in ons eerste ontwerp?}

\item{Moet de motor, rem en locking pins appart bediend kunnen worden?}

\item{Als een onderdeel van de brug (rem, locking pin) kapot gaat, moet de brug dan direct naar de lichten kunnen sturen dat ze aan moeten.}

\end{enumerate}


%----------------------------------------------------------------%

\section{Proposals}
\label{sec:proposals}

\begin{enumerate}
\item{Add one sensor for each light to detect if the lights are working in order to meet the requirement: bariers may not close if lights are not on.}

\item{Add a sensor to detect if there is traffic on the bridge. (To meet requirement \ref{item:traffic})}

\item{Add a third sensor for each of the following sensors, in order to meet the requirement: "the traffic may not be hampered unnecessary".Because the the system can not make a desicion if one sensor gives false information and one sensor gives valid information.}
\begin{itemize}
\item{2 sensors: Bridge is open}
\item{2 sensors: Bridge is closed}
\item{2 sensors: Bridge locking pins state}
\item{2 locking pins}
\end{itemize}
\end{enumerate}



%----------------------------------------------------------------%

\section{ToDo}

Stelling: een bood kan besluiten dat hij er inneens toch niet onderdoor wil, dus vanaf elke volgende state in het systeem moet de vorrige state berijkt kunnen worden. 
Andere case: er kan ook plotseling een tweede boot aankomen als de brug bezig is met sluiten. 
Het opstellen van je systeem op deze manier voorkomt waarschijnlijk ook deadlock. 

\todo[inline]{Zo voeg je commentaar toe}








\end{document}